*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-04 Code/Manuscript_O2.Rmd
edit FtsH table and text

*Prochlorococcus* genomes encode 4 FtsH proteins, henceforth referred to as FtsH1-4, homologs to the characterized FtsH isoforms of the model freshwater cyanobacterium *Synechocystis* FtsH, and with presumably parallel functions (Table \@ref(tab:FtsHTable)). Upon a shift to higher light HLI MED4 upregulated expression of FtsH1 and FtsH2 [@bonisteelStrainSpecificDifferences2018], homologs to the *Synechocystis* slr0228 and slr1604, implicated in PSII repair. In contrast, representative LLIV strain MIT9313 showed less overall expression of the FtsH proteases, and thus has fewer FtsH serving each photosystem.  Furthermore, MIT9313 expressed primarily FtsH3, homologous to *Synechocystis* slr1463 involved in PSI biogenesis, andFtsH expression did not increase in response to light stress in MIT9313. Through adaptation to steady low light, clade LLIV *Prochlorococcus* instead allocate resources to processes other than dynamic regulation of PSII repair.

@@

FtsHTable <- tibble(Organism = c("*Prochlorococcus marinus*", "*Synechocystis sp. PCC6803*", "Function"),
                    FtsH1 = c("FtsH1", "SlrO22", "PSII Repair"),
                    FtsH2 = c("FtsH2", "Slr1604", "PSII Repair"),
                    FtsH3 = c("FtsH3", "Slr1463", "PSI biogenesis"),
                    FtsH4 = c("FtsH4", "Slr1390", "Cell viability")
                    )

>>>>

*Prochlorococcus* genomes encode 4 FtsH proteins, henceforth referred to as FtsH1-4, homologs to the characterized FtsH isoforms of the model freshwater cyanobacterium *Synechocystis* FtsH, and with presumably parallel functions (Table \@ref(tab:FtsHTable)). Upon a shift to higher light HLI MED4 upregulated expression of FtsH1 and FtsH2 [@bonisteelStrainSpecificDifferences2018], homologs to the *Synechocystis* slr0228 and slr1604, implicated in PSII repair. In contrast, representative LLIV strain MIT9313 showed less overall expression of the FtsH proteases, and thus has fewer FtsH serving each photosystem.  Furthermore, MIT9313 expressed primarily FtsH3, homologous to *Synechocystis* slr1463, possibly involved in PSI biogenesis, and FtsH expression did not increase in response to light stress in MIT9313. Through adaptation to steady low light, clade LLIV *Prochlorococcus* instead allocate resources to processes other than dynamic regulation of PSII repair.

@@

FtsHTable <- tibble(Organism = c("*Prochlorococcus marinus*", "*Synechocystis sp. PCC6803*", "Function"),
                    FtsH1 = c("FtsH1", "SlrO228", "PSII Repair"),
                    FtsH2 = c("FtsH2", "Slr1604", "PSII Repair"),
                    FtsH3 = c("FtsH3", "Slr1463", "PSI biogenesis?"),
                    FtsH4 = c("FtsH4", "Slr1390", "Cell viability")
                    )
